\documentclass{book}
\usepackage{sstdef}
\title{qtools}
\begin{document}
\section{Introduction}

\paragraph{\href{How to install qtools}{install.html}}

\paragraph{\href{The \cmd{822body} program}{822body.html}}
\paragraph{\href{The \cmd{822bodyfilter} program}{822bodyfilter.html}}
\paragraph{\href{The \cmd{822headerfilter} program}{822headerfilter.html}}
\paragraph{\href{The \cmd{822headerok} program}{822headerok.html}}

\paragraph{\href{The \cmd{822fields} program}{822fields.html}}
\paragraph{\href{The \cmd{822headers} program}{822headers.html}}

\paragraph{\href{The \cmd{822addr} program}{822addr.html}}
\paragraph{\href{The \cmd{checkaddr} program}{checkaddr.html}}
\paragraph{\href{The \cmd{checkdomain} program}{checkdomain.html}}
\paragraph{\href{The \cmd{ifaddr} program}{ifaddr.html}}
\paragraph{\href{The \cmd{iftoccfrom} program}{iftoccfrom.html}}

\paragraph{\href{The \cmd{filterto} program}{filterto.html}}

\paragraph{\href{The \cmd{condtomaildir} program}{condtomaildir.html}}
\paragraph{\href{The \cmd{tomaildir} program}{tomaildir.html}}

\paragraph{\href{The \cmd{replier} program}{replier.html}}
\paragraph{\href{The \cmd{replier-config} program}{replier-config.html}}

\paragraph{\href{Examples}{examples.html}}

\paragraph{\href{A mailing list for qtools discussion}{../lists.html\#qtools}}


\subsection{What is qtools?}
The qtools package comprises several utilities for use with qmail,
typically as part of \cmd{.qmail} command processing.

\paragraph{\cmd{822body}} extracts the body from a message.

\paragraph{\cmd{822bodyfilter}} filters a message body, preserving the header.

\paragraph{\cmd{822headerfilter}} filters a message header, preserving the body.

\paragraph{\cmd{822headerok}} tests for a well-formed message header.

\paragraph{\cmd{822fields}} extracts field values from a message header.

\paragraph{\cmd{822headers}} extracts field copies from a message header.

\paragraph{\cmd{822addr}} extracts addresses from a message header.

\paragraph{\cmd{checkaddr}} checks an address list for matching addresses.

\paragraph{\cmd{checkdomain}} checks an address list for matching domains.

\paragraph{\cmd{iftoccfrom}} tests for addresses in if, to, cc, and from header fields.

\paragraph{\cmd{filterto}} filters and forwards a message.

\paragraph{\cmd{condtomaildir}} conditionally writes a message to a maildir.

\paragraph{\cmd{tomaildir}} writes a message to a maildir.

\paragraph{\cmd{replier}} is a simple autoreplier.

\paragraph{\cmd{replier-config}} configures \cmd{replier}.

\end{document}
